---
title: "Analyzing the Impact of Ad Strategies"
format: html
editor: visual
---

## Running Code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Install and Load Library

```{r}
# Install these packages if needed
#install.packages(c("tidyverse", "janitor", "broom", "ggplot2", "kableExtra", "knitr", "tidyr"))

library(tidyverse)
library(janitor)
library(broom)
library(ggplot2)
library(kableExtra)
library(knitr)
library(tidyr)
```

#### Simulate Baseline Data

```{r}
set.seed(2025)

n <- 5000
countries <- c("USA", "Canada", "UK", "Nigeria", "India", "Brazil", "Other")

# Define age group weights based on Facebook demographics
age_groups <- c("18-24", "25-34", "35-44", "45-54", "55-64", "65+")
weights <- c(22.1, 30.8, 20.4, 12.3, 8.0, 6.4) # Corresponding percentages for age groups

# Sample age groups based on weights
group_sample <- sample(age_groups, n, replace = TRUE, prob = weights / sum(weights))

# Generate ages within each age group
age <- sapply(group_sample, function(group) {
  if (group == "18-24") round(runif(1, 18, 24))
  else if (group == "25-34") round(runif(1, 25, 34))
  else if (group == "35-44") round(runif(1, 35, 44))
  else if (group == "45-54") round(runif(1, 45, 54))
  else if (group == "55-64") round(runif(1, 55, 64))
  else round(runif(1, 65, 80))
})

# Create the baseline dataset
baseline <- tibble(
  id = 1:n,
  age = age,
  gender = sample(c("Male", "Female", "Non-binary"), n, replace = TRUE, prob = c(0.47, 0.49, 0.04)),
  education_level = sample(c("High school", "Bachelor's", "Master's", "Doctorate"), n, replace = TRUE, prob = c(0.3, 0.35, 0.3, 0.05)),
  income_bracket = sample(c("<30k", "30k–60k", "60k–100k", "100k+"), n, replace = TRUE, prob = c(0.35, 0.25, 0.2, 0.2)),
  urbanicity = sample(c("Urban", "Suburban", "Rural"), n, replace = TRUE, prob = c(0.5, 0.3, 0.2)),
  country = sample(countries, n, replace = TRUE, prob = c(0.25, 0.05, 0.10, 0.15, 0.25, 0.15, 0.05)),
  trust_vaccine = round(runif(n, 1, 5)),  # Likert scale (1: low trust, 5: high trust)
  concern_side_effects = round(runif(n, 1, 5)) # Likert scale (1: low concern, 5: high concern)
)
```

#### Random Assignment to Ad Groups

```{r}
treatment <- tibble(
  id = sample(1:n),
  ad_group = rep(c("Reason", "Emotion", "Control"), length.out = n)
)
```

#### Simulate Endline Data (Post-Ad)

```{r}
# Create IDs for participants who completed the endline survey (10% dropout)
endline_ids <- sample(baseline$id, 4500) # Adjusting column reference to match the baseline dataset

# Simulate the endline dataset 
endline <- baseline %>%
  left_join(treatment, by = "id") %>% 
  filter(id %in% endline_ids) %>%      # Filter for endline participants
  mutate(
    base_prob = 0.5 + 0.1 * (trust_vaccine > 3) - 0.05 * (concern_side_effects > 3),
    ad_effect = case_when(
      ad_group == "Reason" ~ 0.15,
      ad_group == "Emotion" ~ 0.20,
      TRUE ~ 0.00
    ),
    country_effect = case_when(
      country %in% c("Nigeria", "India", "Brazil") ~ -0.02,
      TRUE ~ 0
    ),
    final_prob = pmin(pmax(base_prob + ad_effect + country_effect, 0.1), 0.9), # Bound probabilities
    vaccine_uptake = ifelse(rbinom(n(), size = 1, prob = final_prob) == 1, "Yes", "No"), # Convert uptake to Yes/No
    recall_ad = ifelse(ad_group == "Control", "No", sample(c("Yes", "No"), n(), replace = TRUE)),
    post_trust_vaccine = sample(1:5, n(), replace = TRUE),
    post_concern_side_effects = sample(1:5, n(), replace = TRUE)
  ) %>%
  select(id, recall_ad, post_trust_vaccine, post_concern_side_effects, vaccine_uptake) 
```

#### Merge and Clean the Datasets

```{r}
# Merge the Datasets
final_dataset <- baseline %>%
  left_join(treatment, by = "id") %>%
  left_join(endline, by = "id")

# Clean Dataset

# Convert vaccine_uptake to binary (0/1)
final_dataset$vaccine_uptake_status <- ifelse(final_dataset$vaccine_uptake == "Yes", 1, 0)

final_dataset$vaccine_uptake <- ifelse(is.na(final_dataset$vaccine_uptake), "No Response", final_dataset$vaccine_uptake)

# Clean Dataset
cleaned_dataset <- final_dataset %>%
  filter(if_all(where(is.numeric), ~ !is.na(.) & is.finite(.)))
```

#### Save Dataset

```{r}
dir.create("data")
write_csv(baseline, "data/baseline_survey.csv")
write_csv(treatment, "data/treatment_assignment.csv")
write_csv(endline, "data/endline_survey.csv")
write_csv(final_dataset, "data/final_dataset.csv")
write_csv(cleaned_dataset, "data/cleaned_dataset.csv")
```

#### Demographics Summary

```{r}
# Demographics by Ad Group
demographics_summary <- final_dataset %>%
  group_by(ad_group) %>%
  summarise(
    Mean_Age = round(mean(age), 1),
    Female = round(mean(gender == "Female") * 100, 1),
    Male = round(mean(gender == "Male") * 100, 1),
    College_Grad = round(mean(education_level %in% c("Doctorate", "Master's", "Bachelor's")) * 100, 1),
    High_Income = round(mean(income_bracket == "100k+") * 100, 1),
    Low_Income = round(mean(income_bracket == "<30k") * 100, 1)
  )

kable(demographics_summary, caption = "Table 1: Demographics by Ad Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r}
# Demographics by Country
country_distribution <- final_dataset %>%
  group_by(country) %>%
  summarise(
    Count = n()
  ) %>%
  mutate(Percentage = round(Count / sum(Count) * 100, 1))

kable(country_distribution, caption = "Table 2: Country Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Analysis and Visualization

### Tables

#### Logistic Regression

```{r}
# Logistic regression
model <- glm(
  vaccine_uptake_status ~ ad_group + gender + education_level + income_bracket + urbanicity + country + age,
  data = final_dataset,
  family = "binomial"
)
summary(model)
```

#### Summary Statistics for Trust and Side Effect Concerns

```{r}
# Summary statistics for trust in vaccine and concern about side effects
summary_trust_concern <- final_dataset %>%
  summarise(
    avg_trust = mean(trust_vaccine),
    sd_trust = sd(trust_vaccine),
    avg_concern = mean(concern_side_effects),
    sd_concern = sd(concern_side_effects)
  )

kable(summary_trust_concern, caption = "Table 3: Summary Statistics for Trust in Vaccine and Concern about Side Effects") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Vaccine Uptake Distribution by Ad Group

```{r}
# Summary table
vaccine_uptake_distribution_by_ad_group <- cleaned_dataset %>%
  tabyl(ad_group, vaccine_uptake) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns()

kable(vaccine_uptake_distribution_by_ad_group, caption = "Table 4: Vaccine Uptake Distribution by Ad Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Vaccine Uptake by Education Level

```{r}
# Vaccine Uptake by Education Level
vaccine_uptake_by_education_level <- cleaned_dataset %>%
  group_by(education_level) %>%
  summarize(
    uptake_rate = round(mean(vaccine_uptake_status, na.rm = TRUE) * 100, 1),
    .groups = 'drop'
  )

kable(vaccine_uptake_by_education_level, caption = "Table 5: Vaccine Uptake by Education Level") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Vaccine Uptake by Country and Treatment Group

```{r}
# Vaccine Uptake Rate by Country and Treatment Group (Ad Strategy)
vaccine_uptake_by_country_and_ad_group <- cleaned_dataset %>%
  group_by(country, ad_group) %>%
  summarize(
    uptake_rate = round(mean(vaccine_uptake_status, na.rm = TRUE) * 100, 1),
    .groups = 'drop'
  ) %>%
  pivot_wider(names_from = ad_group, values_from = uptake_rate)

kable(vaccine_uptake_by_country_and_ad_group, caption = "Table 6: Vaccine Uptake Rate by Country and Ad Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Vaccine Uptake by Ad Group and Trust Level

```{r}
# Summary table showing vaccine uptake by ad group and trust level (Low, Medium, High trust)
vaccine_uptake_by_trust_level <- cleaned_dataset %>%
  mutate(trust_level = case_when(
    trust_vaccine <= 2 ~ "Low",
    trust_vaccine <= 4 ~ "Medium",
    TRUE ~ "High"
  )) %>%
  group_by(ad_group, trust_level) %>%
  summarize(
    uptake_rate = round(mean(vaccine_uptake_status, na.rm = TRUE) * 100, 1),
    .groups = 'drop'
  )


kable(vaccine_uptake_by_trust_level, caption = "Table 7: Vaccine Uptake by Ad Group and Trust Level") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Vaccine Uptake by Income Bracket and Ad Group

```{r}
# Summary table showing vaccine uptake rate by income bracket and ad group
vaccine_uptake_by_income_bracket <- cleaned_dataset %>%
  group_by(income_bracket, ad_group) %>%
  summarize(
    uptake_rate = round(mean(vaccine_uptake_status, na.rm = TRUE) * 100, 1),
    .groups = 'drop'
  )

kable(vaccine_uptake_by_income_bracket, caption = "Table 8: Vaccine Uptake Rate by Income Bracket and Ad Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Proportions of Vaccine Uptake by Ad Group and Gender

```{r}
# Table showing proportions of vaccine uptake by ad group and gender
vaccine_uptake_by_ad_group_gender <- cleaned_dataset %>%
  group_by(ad_group, gender) %>%
  summarize(
    uptake_proportion = round(mean(vaccine_uptake_status, na.rm = TRUE) * 100, 1), 
    .groups = 'drop'
  )

kable(vaccine_uptake_by_ad_group_gender, caption = "Table 9: Proportions of Vaccine Uptake by Ad Group and Gender") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Side Effect Concerns by Age Group

```{r}
# Table showing concern about side effects by age group
concern_by_age_group <- final_dataset %>%
  mutate(age_group = cut(age, breaks = c(18, 25, 35, 45, 55, 65, Inf), labels = c("18-24", "25-34", "35-44", "45-54", "55-64", "65+"), right = FALSE)) %>%
  group_by(age_group) %>%
  summarize(
    avg_concern = round(mean(concern_side_effects, na.rm = TRUE), 2),
    .groups = 'drop'
  )

kable(concern_by_age_group, caption = "Table 10: Concern About Side Effects by Age Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Side Effect Concerns by Country

```{r}
# Table showing concern about side effects by country
concern_by_country <- final_dataset %>%
  group_by(country) %>%
  summarize(
    avg_concern = round(mean(concern_side_effects, na.rm = TRUE), 2), 
    .groups = 'drop'
  )

kable(concern_by_country, caption = "Table 11: Concern About Side Effects by Country") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Trust in Vaccine by Ad Group and Country

```{r}
# Summary table for trust in vaccine by ad group and country
trust_by_ad_group_and_country <- final_dataset %>%
  group_by(ad_group, country) %>%
  summarize(
    avg_trust = round(mean(trust_vaccine, na.rm = TRUE), 2), 
    .groups = 'drop'
  )

kable(trust_by_ad_group_and_country, caption = "Table 12: Trust in Vaccine by Ad Group and Country") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Export Tables to CSV Files

```{r}
dir.create("table")
write_csv(demographics_summary, "table/demographics_summary.csv")
write_csv(country_distribution, "table/country_distribution.csv")
write_csv(vaccine_uptake_distribution_by_ad_group, "table/vaccine_uptake_distribution_by_ad_group.csv")
write_csv(summary_trust_concern, "table/summary_trust_concern.csv")
write_csv(vaccine_uptake_by_education_level, "table/vaccine_uptake_by_education_level.csv")
write_csv(vaccine_uptake_by_country_and_ad_group, "table/vaccine_uptake_by_country_and_ad_group.csv")
write_csv(vaccine_uptake_by_trust_level, "table/vaccine_uptake_by_trust_level.csv")
write_csv(vaccine_uptake_by_income_bracket, "table/vaccine_uptake_by_income_bracket.csv")
write_csv(vaccine_uptake_by_ad_group_gender, "table/vaccine_uptake_by_ad_group_gender.csv")
write_csv(concern_by_age_group, "table/concern_by_age_group.csv")
write_csv(concern_by_country, "table/concern_by_country.csv")
write_csv(trust_by_ad_group_and_country, "table/trust_by_ad_group_and_country.csv")
```

### Plots

#### Marginal Effects Plot

```{r}
# Effect of Ad Group on Vaccine Uptake
plot_data <- tidy(model, exponentiate = TRUE, conf.int = TRUE) %>%
  filter(str_detect(term, "ad_group")) %>%
  add_row(term = "ad_groupControl", estimate = 1, conf.low = 1, conf.high = 1)

ad_group_effect_plot <- ggplot(plot_data, aes(x = term, y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange() +
  geom_hline(yintercept = 1, linetype = "dashed") +
  labs(
    title = "Effect of Ad Group on Vaccine Uptake (Odds Ratio)",
    x = "Ad Group",
    y = "Odds Ratio"
  ) +
  theme_minimal()

print(ad_group_effect_plot)
```

#### Vaccine Uptake by Ad Group and Country

```{r}
vaccine_uptake_plot <- ggplot(cleaned_dataset, aes(x = ad_group, fill = factor(vaccine_uptake))) +
  geom_bar(position = "fill") +
  facet_wrap(~ country) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Vaccine Uptake by Ad Group and Country",
    y = "Proportion",
    fill = "Vaccine Uptake"
  ) +
  theme_minimal()

print(vaccine_uptake_plot)
```

#### Vaccine Uptake by Age Group

```{r}
vaccine_uptake_age_group_plot <- cleaned_dataset %>%
  mutate(age_group = cut(
    age,
    breaks = c(18, 25, 35, 45, 55, 65, Inf),
    labels = c("18-24", "25-34", "35-44", "45-54", "55-64", "65+"),
    right = FALSE
  )) %>%
  ggplot(aes(x = age_group, fill = factor(vaccine_uptake))) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Vaccine Uptake by Age Group",
    x = "Age Group",
    y = "Proportion",
    fill = "Uptake"
  ) +
  theme_minimal()

print(vaccine_uptake_age_group_plot)

```

#### Trust in Vaccine by Ad Group

```{r}
# Create the plot and name it `trust_distribution_plot`
trust_distribution_plot <- ggplot(final_dataset, aes(x = trust_vaccine, fill = ad_group)) +
  geom_histogram(binwidth = 1, position = "dodge") +
  labs(
    title = "Distribution of Trust in Vaccine by Ad Group",
    x = "Trust in Vaccine (1-5)",
    y = "Count"
  ) +
  theme_minimal()

print(trust_distribution_plot)
```

#### Change in Trust in Vaccine

```{r}
# Create the long dataset for visualization
long_dataset <- cleaned_dataset %>%
  pivot_longer(cols = c(trust_vaccine, post_trust_vaccine), 
               names_to = "time_period", values_to = "value")

# Create the plot
trust_change_plot <- ggplot(long_dataset, aes(x = time_period, y = value, group = id)) +
  geom_line(aes(color = ad_group), alpha = 0.5) +
  stat_summary(fun = mean, geom = "line", aes(group = ad_group), color = "black", size = 1.5) +
  labs(
    title = "Change in Trust in Vaccine Before and After Ad Exposure",
    x = "Time Period",
    y = "Trust in Vaccine (1-5)"
  ) +
  theme_minimal()

print(trust_change_plot)
```

#### Change in Trust in Vaccine Density Plot

```{r}
trust_density_plot <- ggplot(cleaned_dataset, aes(x = trust_vaccine, fill = "Before")) +
  geom_density(alpha = 0.4, color = NA) +
  geom_density(aes(x = post_trust_vaccine, fill = "After"), alpha = 0.4, color = NA) +
  facet_wrap(~ ad_group) +
  labs(
    title = "Distribution of Trust in Vaccine Before and After Ad Exposure",
    x = "Trust in Vaccine (1-5)",
    y = "Density"
  ) +
  theme_minimal()

print(trust_density_plot)
```

#### Country-wise Vaccine Uptake Rates

```{r}
vaccine_uptake_country_plot <- cleaned_dataset %>%
  group_by(country) %>%
  summarize(uptake_rate = mean(vaccine_uptake_status, na.rm = TRUE)) %>%
  ggplot(aes(x = reorder(country, uptake_rate), y = uptake_rate)) +
  geom_col(fill = "steelblue") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Vaccine Uptake Rate by Country",
    x = "Country",
    y = "Uptake Rate"
  ) +
  coord_flip() +
  theme_minimal()

print(vaccine_uptake_country_plot)
```

#### Concern About Side Effects by Country

```{r}
concern_side_effects_plot <- ggplot(final_dataset, aes(x = concern_side_effects, fill = country)) +
  geom_density(alpha = 0.4) +
  labs(
    title = "Concern About Side Effects by Country",
    x = "Concern Level (1-5)",
    y = "Density"
  ) +
  theme_minimal()

print(concern_side_effects_plot)

```

#### Save Plots

```{r}
dir.create("plots")
ggsave("plots/ad_group_effect_plot.png", plot = ad_group_effect_plot, width = 8, height = 6)
ggsave("plots/vaccine_uptake_plot.png", plot = vaccine_uptake_plot, width = 8, height = 6)
ggsave("plots/vaccine_uptake_age_group_plot.png", plot = vaccine_uptake_age_group_plot, width = 8, height = 6)
ggsave("plots/trust_distribution_plot.png", plot = trust_distribution_plot, width = 8, height = 6)
ggsave("plots/trust_change_plot.png", plot = trust_change_plot, width = 8, height = 6)
ggsave("plots/trust_density_plot.png", plot = trust_density_plot, width = 8, height = 6)
ggsave("plots/vaccine_uptake_country_plot.png", plot = vaccine_uptake_country_plot, width = 8, height = 6)
ggsave("plots/concern_side_effects_plot.png", plot = concern_side_effects_plot, width = 8, height = 6)
```
